Dynein walks like an Imperial AT-ST

### 2018-08-16 papers/paper/paper.tex
Add new better model figure which shows realistic dynein full-length structure from Grotjahn et al 2018

\begin{figure*}[tbhp]
\includegraphics[width=0.3\linewidth]{../../plots/burgess-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/redwine-model-figure.pdf}%
\includegraphics[width=0.3\linewidth]{../../plots/chowdhury-model-figure.pdf}%
\includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}. \textit{Grey bg:} Model superimposed over a native dynein micrograph \cite{nativestructure}. \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point. Orange indicates the linker region used to dock the two monomers. Left figure has a scale bar of 15nm, middle 25nm and right 28.8nm between the two binding domains.}
\label{fig:duration-length}
\end{figure*}

@@

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & & \cite{burgess-paper}\\
$L_t$ & $\lt nm$ & & \cite{burgess-paper}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\
$D$ & 0.2 nm &  & \\

>>>>

\begin{figure}[tbhp]
\includegraphics[width=0.4\linewidth]{../../plots/burgess-model-figure.pdf}%
\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}. \textit{Grey bg:} Model superimposed over full-length dimerized dynein bound to accessory proteins \cite{grotjahn}. }
\label{fig:duration-length}
\end{figure}

%% \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point. Orange indicates the linker region used to dock the two monomers. Left figure has a scale bar of 15nm, middle 26.3nm and right 28.8nm between the two binding domains.

@@

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & & \\
$L_s$ & $\ls nm$ & 21nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
$L_t$ & $\lt nm$ & 23nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{burgess-paper}\\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{burgess-paper}\\
$\theta_t$ & $\eqt$ &  & \\
$R_t$ & $\radiust$ & 8nm & \cite{burgess-paper}\\
$R_m$ & $\radiusm$ & 11nm & \cite{burgess-paper}\\
$R_b$ & $\radiusb$ & 3.5nm & \cite{burgess-paper}\\
